% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\增加{Not from the original}{Since I'm using Linux OS, there are some compatibility problems with my PDF viewer, which require a lot of time to solve, I change the method and re-type the article by \LaTeX{}, therefore I can use ``changes'' package to achieve the same function, please forgive me.}

\注释{The line spacing of the original article is a bit large.}
\注释{Some words of the section title needs to be capitalized, say ``The Title of the Article''.}

This book mainly introduces how to write mathematical articles in English, and this chapter particularly explains the structure of mathematical articles. The main points of each part according to the sections of the article are as followings.

\section{The title of the article}
The title of the article should convey the message to the reader, and should be specific and clear enough, preferably reflecting the main contribution of the article. In addition, the title of the article should not refer to a large direction, but to have a certain difference with the existing title and contain a certain amount of information, \替换{``so that'' is not adverb}{so}{so that} readers can easily find your article through the search engine, which can grab the \替换{someone's attention}{readers'}{readers} attention much better. For readers, the title of the article determines whether it is necessary to continue reading, and it helps judge the main contribution and innovation of the article. Besides, it determines the type of article as well.

\section{The abstract of the article}
The abstract of the article should be able to accurately and concisely summarize the main purpose, ideas and results of the article. When writing abstracts, it is important to avoid mathematical notation and use narrative language. Secondly, giving full information about someone else's article when quoting \删除{subject exists (已有主语)}{it} is necessary. \替换{``what's more'' is a spoken phrase?}{Moreover}{What is more}, abstract of the article should give sufficient information about the main results. For review, the abstract must point out the article's new contribution. Notably, starting with phrases like In this paper or this paper should be avoided.

\section{The introduction of the article}
The introduction should conclude a comprehensive, accurate and objective explanation of the background material and \增加{add a quantifier}{a} brief development of the issue, \替换{}{``contributions of people'' is better?}{people's contributions} to it, the motivation for writing the article, and the main results of the article. It should be plain and to the point, avoid mathematical notation and generalities. \替换{maybe a typo}{Moreover}{Whats more}, the middle of the introduction usually includes definitions of the problem which is meant to be solved, summarization of the main achievements achieved in the past and their shortcomings, and the main methods people have used. And then\替换{maybe a typo}{,}{.} the end of the introduction generally summarizes each \替换{each + singular?}{section}{sections} of the main body.

\section{The body of the article}
\注释{The structure of this section is somewhat difficult to read, maybe you can display them in a list format. Moreover, pay attention to the case of the side-by-side sentences (注意并列关系句子的大小写及词性).}
The main body of the paper comprehensively presents the author's research results, the demonstration and reasoning process of new results, or the construction process of new methods, theoretical analysis and numerical experiments. For the strong theoretical articles, the body can be divided into preliminary knowledge (Preliminaries), the introduction of symbol concept description and definition; Main results: the main results are derived, analyzed and discussed, \删除{``and'' is too much}{and} the outline of proof and extensions are included. Calculate or articles of applied mathematics generally includes the problem or governing equations; numerical method or experimental method; theoretical analysis; the numerical results; \增加{the last one uses ``and''}{and} conclusions.

\section{The conclusion of the article}
\注释{pay attention to the case of the side-by-side sentences (注意并列关系句子的大小写及词性).}
The conclusion should include: a brief introduction to the main contributions of the article; \替换{case of words and part of speech (词性与大小写)}{explanation of the problems}{Explain the problems} mentioned in the introduction; Point out the problem that the article does not consider; Talk about the possible impact of the job and the benefits of solving other related problems, and look ahead to the future work. In addition, when writing the conclusion, you should also be careful not to be too modest or exaggerate the achievements, do not introduce new ideas, \替换{part of speech}{problems that is difficult to solve}{difficult to solve problems} and contradictory views or conclusions, and avoid repeating the introduction.

After that, it also introduces the acknowledgements, references, appendix and signed part, but they are all omitted for reasons of importance and length.
