% !Mode:: "TeX:UTF-8"
% !TEX program  = xelatex
\newgeometry{margin=1.6in, marginpar=1.5in}

\增加{Not from the original}{Since I'm using Linux OS, there are some compatibility problems with my LibreOffice viewer, which require a lot of time to solve, I change the method and re-type the article by \LaTeX{}, therefore I can use ``changes'' package to achieve the same function. By the way, I check this article through \href{https://docs.qq.com}{QQ Docs}.}

\注释{Please mind the indentation before the paragraph.}
\注释{Change \texttt{magazine} to \texttt{journal}, maybe you use some translator?}

Excellent articles are for others to read. After the article is finished, the author should consider submitting a manuscript to the magazine for publication. But the author gives us an important suggestion, \注释{\texttt{do not} or \texttt{don't}?}don't post something that is not worth publishing. Next, the article provides you with some technical considerations for submitting. 


\section{Submission preparation}
Submission is the next step after the article is written and revised repeatedly. The most important question is which magazine to \替换{Google Translate maybe?}{choose}{vote for}. As the Tang and Ding say, the author should reasonably select the submitted magazine according to the content and subjective wishes of the article, and combine the academic grades of the magazine, the annual publishing cycle, the average review time, and the publication time of the paper to find the balance of satisfaction.


\section{Submission process}
When you select a magazine for submission, you will enter the process of submission. The process usually concludes \增加{An article is missing.}{the} following parts:
\begin{enumerate}
	\item Read the magazine's guide to the author.\注释{Please mind the punctuations.}
	\item Write a cover letter.
	\item Send the manuscript.
	\item Manuscript review.
\end{enumerate}


\section{Reviewers' comments}
When you receive the review report, you should read the report very carefully. If you intend to work with the magazine, you should respond to all the \替换{}{problems}{problem} items listed in the report one by one. After the revision of the article, the same procedure for the first submission will be repeated. The last modified date will be listed on the front page, the word revised will be marked, a new submission letter will be attached, and it will be sent back to the magazine editor \增加{Sentence is incomplete.}{who is} responsible for the manuscript.


\section{Articles published}
You should send back the proofreading within the stipulated time, otherwise\增加{Missing a comma after the introductory phrase.}{,} the publication time may be delayed. In the end, when you see your paper appear in a new issue of magazines, you should be happy.
